Contribution of computational intelligence tools \\ in the improvement of strategy games

### 2018-02-27 article.tex
Add files via upload

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

@@

\usepackage{tikz}
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\subsection{Planet War}
As we mentioned previously one of the international AI competition is organized by google community. In 2010 google choose like a game planet wars for it AI challenge competition. In this pager, we work with a version of Glacon game in order to design a fighter bots. A planet war match\cite{doc1} runs on a map with several distributed planets in different positions, such as each of them has a number describes the quantity of starships its owns. In each turn, the number of starship will change. Each planet is owned by a player, opponent or neutral planet(owned by nobody), moreover, each planet belongs to the player (no neutral one) will increase their number of starships after each step according to their growth rate, this rate explain the additional starship's number will generate each planet in each step.
The main purpose of the planet war game\cite{doc1} is to challenge all players and try to defeat all of them, that mean to destroy all enemy's starships. Planet war is an RTS game by its nature. to achieve a specific objective each player has a limit number of turns to do it and try to win (beat opponent).  \\

\begin{figure}
\begin{tikzpicture}
\draw [fill =gray, ultra thick, gray] (2,1) circle [radius=0.3];
\node at (2,1) {14};
\draw [fill =gray, ultra thick, gray] (3,2) circle [radius=0.4];
\draw [fill = gray ,thick] (3.5,2.8) to (3.7,2.7) to (3.8,3.2) to (3.5,2.8);
\node at (3.5,2.5) {20};
\node at (3,2) {29};
\draw [fill =gray, ultra thick, gray] (4,1) circle [radius=0.3];
\node at (4,1) {45};
\draw [fill =gray ,thick] (3,1.1) to (3,0.9) to (2.7,1) to (3,1.1);
\node at (3.2,1) {12};
\draw [fill =gray, ultra thick, gray] (6,0.3) circle [radius=0.3];
\node at (6,0.3) {12};
\draw [fill =gray, ultra thick, gray] (8.5,1.5) circle [radius=0.6];
\node at (8.5,1.5) {33};
\draw [fill = gray ,thick] (7.3,1.6) to (6.9,1.5) to (7.3,1.4) to (7.3,1.6);
\node at (7.6,1.5) {10};
\draw [fill =gray, ultra thick, gray] (8,3.5) circle [radius=0.3];
\node at (8,3.5) {18};
\draw [fill =gray, ultra thick, gray] (6.5,4.5) circle [radius=0.6];
\node at (6.5,4.5) {9};
%\draw [fill =lightgray, ultra thick, lightgray] (3.5,3) circle [radius=0.3];
%\node at (3.5,3) {78};
\draw [fill =lightgray, ultra thick, lightgray] (5.5,1.5) circle [radius=0.6];
\node at (5.5,1.5) {136};
\draw [fill =lightgray, ultra thick, lightgray] (5.5,3) circle [radius=0.4];
\node at (5.5,3) {67};
\draw [fill =lightgray, ultra thick, lightgray] (7,2.5) circle [radius=0.3];
\node at (7,2.5) {78};
\draw [fill =lightgray, ultra thick, lightgray] (5.5,7.5) circle [radius=0.6];
\node at (5.5,7.5) {102};
\draw (1,3.2) circle [radius=0.3];
\node at (1,3.2) {88};
\draw [thick] (1.1,2.5) to (1.3,2.6) to (1.3,2.2) to (1.1,2.5);
\draw [thick] (1.3,1.8) to (1.5,1.9) to (1.5,1.5) to (1.3,1.8);
\node at (1.2,2.7) {8};
\node at (1.3,2) {8};
\draw  (1,5.5) circle [radius=0.4];
\node at (1,5.5) {8};
\draw  (2.5,4.8) circle [radius=0.6];
\node at (2.5,4.8) {10};
\draw  (3.2,7) circle [radius=0.3];
\draw [thick] (3.3,5.7) to (3.7,5.9) to (3.5,5.5) to (3.3,5.7);
\draw [thick] (4.2,6.5) to (4.6,6.7) to (4.4,6.3) to (4.2,6.5);
\node at (3.1,5.4) {15};
\node at (4,6.2) {10};
\node at (3.2,7) {15};
\draw  (4.5,4) circle [radius=0.4];
\node at (4.5,4) {2};
\draw  (5.5,6) circle [radius=0.3];
\node at (5.5,6) {45};
\draw  (8,6.5) circle [radius=0.5];
\draw [thick] (8,5.5) to (8.2,5.5) to (8.1,5.1) to (8,5.5);
\draw [thick] (8,4.5) to (8.2,4.5) to (8.1,4.1) to (8,4.5);
\node at (8,6.5) {1};
\node at (8.1,5.7) {2};
\node at (8.1,4.7) {8};
\end{tikzpicture}
\caption{Simulated of an early stage of a run in Planet Wars. White planets belongs to the player (blue color in the game), dark grey belong to the opponent (red in the game), and light grey planets belong to no player. The triangles are fleets, and the numbers (in planets and triangles) represent the
starships.}
\end{figure}

Moreover, the bot's design faces two major problems: the first one \cite{doc1}is that the bot can't store any information about its previous turns like actions it did, actions of its opponent or even the map's state. Since in each turn, the bot meets with an unknown map as it just begins the game for the first time. The second one\cite{doc3} is that the time requires to move(make an action) is just one second. So these difficulties make the bot's design like a great challenge. In this kind of game, everything has a sum of properties\cite{doc1}. Such as, planets have the x and y coordination for their locations in the map, ownersID, number of starship and growth rate. To conquest other planets, the player needs to send fleets for this aim.Each fleet has a playerID parameter, number of starships, source planetID, destination planetID, turn's number need to reach the target. In each simulated turn\cite{doc1}, the player has the ability to send fleets in a battle with other planet's starships with the source planetID and target planetID, while, the player has the ability\cite{doc1} to make just one action per turn. After each move (action) the planets belong to the players\cite{doc5} increase their ship's number according to their growth rate. To make fleets previously sent reach enemies planets its take time of many turns according to the distance between the source planet and the target planet, moreover, if the source and target planet owned by the same player then it considered like a reinforcment\cite{doc1,doc5} by adding the ship's number on the fleet to the number hosted on the target planet. when the fleets reach the target its will make battles with local target ships, otherwise, if the target is a neutral planet, the player must to sends at least one additional ship to own the planet. While, if the target is owned by the enemy the two players will fight until one with the highest starship number owns the planet. When the player sent fleets to reach some goals\cite{doc5}, he can't change their directions. In addition, the player can send more fleet in the next turns even that the first ones do not yet arrive at their destinations. In the end of the match\cite{doc5}, the player with the highest number of starships wins. If a player loses all their starships then the game will end also faster. whilst, the players have the same starship's number at the end of the game there is a draw\cite{doc5}. 
\subsection{immune system overview}

@@

\begin{figure}
\begin{tabular}{c}
\includegraphics[scale = 0.9]{clonaS}
\end{tabular}
\caption{Clonal selection mechanism}
\end{figure}

@@

\subsection{Artificial Immune System}
Inspiring from the biological immune system an algorithm has been developed called Artificial Immune System (AIS)\cite{doc6}. The search technic is similar to the natural immune system by the implication between the fitness function and the affinity maturation in the natural system.
\subsubsection{Initialisation}
A random population N is generated in the search space, as a process that used in the other heuristic algorithms. This population considered like antibodies.
\subsubsection{Clonal proliferation}
In this step, the antibodies will clone (proliferate) according to their fitness(affinity).
\subsubsection{Maturation}
The maturation technic is similar to the mutation one with a mutation probability P. this mutation is applied to equation (1) : 
\begin{equation}
x_{id} = x_{id} + k(x_{d_{max}} - x_{d_{min}}) . N(0,1)
\end{equation}
where $x_{id}$ represent the dimension d of the antibody i, $x_{max}$ and $x_{min}$ represent the min and the max bounds of the variable i, N(0,1) is the standard distribution and k is the scale factor.
\subsubsection{Evaluation}
In the evaluation step, the fitness function of every antibody is calculated by computing the affinity values.
\subsubsection{Ageing operator}
This factor is used to eliminate the individuals lost more. Indeed, the Ageing operator leads to upgrading the initial population.
\subsection{AIS pseudocode}
\begin{figure}
\begin{tikzpicture}
\draw [thick] (4.5,20) circle [radius=0.5];
\node at (4.5,20) {Start};
\draw [->] [thick](4.5,19.5) -- (4.5,19);
\draw (2,19) --(8,19);
\draw (1,18.5) --(7,18.5);
\draw (2,19) --(1,18.5);
\draw (8,19) --(7,18.5);
\node at (4.5,18.7) {AIS parameters};
\draw [->] [thick](4.5,18.5) -- (4.5,18);
\draw (1,18) --(8.5,18);
\draw (1,17.5) --(8.5,17.5);
\draw (1,18) --(1,17.5);
\draw (8.5,18) --(8.5,17.5);
\node at (4.5,17.7) {Random antibodies initialisation};
\draw [->] [thick](4.5,17.5) -- (4.5,17);
\draw (1,17) --(8.5,17);
\draw (1,16.5) --(8.5,16.5);
\draw (1,17) --(1,16.5);
\draw (8.5,17) --(8.5,16.5);
\node at (4.5,16.7) {Clonal proliferation};
\draw [->] [thick](4.5,16.5) -- (4.5,16);
\draw (1,16) --(8.5,16);
\draw (1,15.5) --(8.5,15.5);
\draw (1,15.5) --(1,16);
\draw (8.5,15.5) --(8.5,16);
\node at (4.5,15.7) {Maturation};
\draw [->][thick] (4.5,15.5) -- (4.5,15);
\draw (1,15) --(8.5,15);
\draw (1,14.5) --(8.5,14.5);
\draw (1,14.5) --(1,15);
\draw (8.5,14.5) --(8.5,15);
\node at (4.5,14.7) {Antibodies evaluation};
\draw [->][thick] (4.5,14.5) -- (4.5,14);
\draw (1,14) --(8.5,14);
\draw (1,13.5) --(8.5,13.5);
\draw (1,13.5) --(1,14);
\draw (8.5,13.5) --(8.5,14);
\node at (4.5,13.7) {Ageing operator};
\draw [->][thick] (4.5,13.5) -- (4.5,13);
\draw (1,13) --(8.5,13);
\draw (1,12.5) --(8.5,12.5);
\draw (1,12.5) --(1,13);
\draw (8.5,12.5) --(8.5,13);
\node at (4.5,12.7) {best individuals selection};
\draw [->][thick] (4.5,12.5) -- (4.5,12);
\draw (4.5,12) --(2.5,11.5);
\draw (2.5,11.5) --(4.5,11);
\draw (4.5,11) --(6.5,11.5);
\draw (6.5,11.5) --(4.5,12);
\node at (4.5,11.5) {Stopping criterion};
\draw (2.5,11.5) --(0.7,11.5);
\draw (0.7,11.5) --(0.7,17.3);
\node at (4.1,10.7) {Yes};
\node at (2.2,11.8) {No};
\draw [->][thick] (0.7,17.3) -- (4.5,17.3);
\draw [->][thick] (4.5,11) -- (4.5,10.5);
\draw (1.5,10.5) --(7.5,10.5);
\draw (1.5,9.8) --(7.5,9.8);
\draw (1.5,10.5) --(1.5,9.8);
\draw (7.5,10.5) --(7.5,9.8);
\node at (4.5,10.1) {Output optimal solution};
\draw [->][thick](4.5,9.8) -- (4.5,9.3);
\draw [thick](4.5,8.8) circle [radius=0.5];
\node at (4.5,8.8) {End};
\end{tikzpicture}
\caption{AIS diagram}
\end{figure}

>>>>

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double 
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

@@

\usepackage{tikz}
\usepackage{pdfpages}
\usepackage{pgfplots}
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\section{Planet War}
As we mentioned previously one of the international AI competition is organized by google community. In 2010 google choose like a game planet wars for it AI challenge competition. In this pager, we work with a version of Glacon game in order to design a fighter bots. A planet war match\cite{doc1} runs on a map with several distributed planets in different positions, such as each of them has a number describes the quantity of starships its owns. In each turn, the number of starship will change. Each planet is owned by a player, opponent or neutral planet(owned by nobody), moreover, each planet belongs to the player (no neutral one) will increase their number of starships after each step according to their growth rate, this rate explain the additional starship's number will generate each planet in each step.
The main purpose of the planet war game\cite{doc1} is to challenge all players and try to defeat all of them, that mean to destroy all enemy's starships. Planet war is an RTS game by its nature. to achieve a specific objective each player has a limit number of turns to do it and try to win (beat opponent).  \\

\begin{figure}
\begin{tikzpicture}[scale = 0.8]
\draw [fill =gray, ultra thick, gray] (2,1) circle [radius=0.3];
\node at (2,1) {14};
\draw [fill =gray, ultra thick, gray] (3,2) circle [radius=0.4];
\draw [fill = gray ,thick] (3.5,2.8) to (3.7,2.7) to (3.8,3.2) to (3.5,2.8);
\node at (3.5,2.5) {20};
\node at (3,2) {29};
\draw [fill =gray, ultra thick, gray] (4,1) circle [radius=0.3];
\node at (4,1) {45};
\draw [fill =gray ,thick] (3,1.1) to (3,0.9) to (2.7,1) to (3,1.1);
\node at (3.2,1) {12};
\draw [fill =gray, ultra thick, gray] (6,0.3) circle [radius=0.3];
\node at (6,0.3) {12};
\draw [fill =gray, ultra thick, gray] (8.5,1.5) circle [radius=0.6];
\node at (8.5,1.5) {33};
\draw [fill = gray ,thick] (7.3,1.6) to (6.9,1.5) to (7.3,1.4) to (7.3,1.6);
\node at (7.6,1.5) {10};
\draw [fill =gray, ultra thick, gray] (8,3.5) circle [radius=0.3];
\node at (8,3.5) {18};
\draw [fill =gray, ultra thick, gray] (6.5,4.5) circle [radius=0.6];
\node at (6.5,4.5) {9};
%\draw [fill =lightgray, ultra thick, lightgray] (3.5,3) circle [radius=0.3];
%\node at (3.5,3) {78};
\draw [fill =lightgray, ultra thick, lightgray] (5.5,1.5) circle [radius=0.6];
\node at (5.5,1.5) {136};
\draw [fill =lightgray, ultra thick, lightgray] (5.5,3) circle [radius=0.4];
\node at (5.5,3) {67};
\draw [fill =lightgray, ultra thick, lightgray] (7,2.5) circle [radius=0.3];
\node at (7,2.5) {78};
\draw [fill =lightgray, ultra thick, lightgray] (5.5,7.5) circle [radius=0.6];
\node at (5.5,7.5) {102};
\draw (1,3.2) circle [radius=0.3];
\node at (1,3.2) {88};
\draw [thick] (1.1,2.5) to (1.3,2.6) to (1.3,2.2) to (1.1,2.5);
\draw [thick] (1.3,1.8) to (1.5,1.9) to (1.5,1.5) to (1.3,1.8);
\node at (1.2,2.7) {8};
\node at (1.3,2) {8};
\draw  (1,5.5) circle [radius=0.4];
\node at (1,5.5) {8};
\draw  (2.5,4.8) circle [radius=0.6];
\node at (2.5,4.8) {10};
\draw  (3.2,7) circle [radius=0.3];
\draw [thick] (3.3,5.7) to (3.7,5.9) to (3.5,5.5) to (3.3,5.7);
\draw [thick] (4.2,6.5) to (4.6,6.7) to (4.4,6.3) to (4.2,6.5);
\node at (3.1,5.4) {15};
\node at (4,6.2) {10};
\node at (3.2,7) {15};
\draw  (4.5,4) circle [radius=0.4];
\node at (4.5,4) {2};
\draw  (5.5,6) circle [radius=0.3];
\node at (5.5,6) {45};
\draw  (8,6.5) circle [radius=0.5];
\draw [thick] (8,5.5) to (8.2,5.5) to (8.1,5.1) to (8,5.5);
\draw [thick] (8,4.5) to (8.2,4.5) to (8.1,4.1) to (8,4.5);
\node at (8,6.5) {1};
\node at (8.1,5.7) {2};
\node at (8.1,4.7) {8};
\end{tikzpicture}
\caption{Simulated of an early stage of a run in Planet Wars. White planets belongs to the player (blue color in the game), dark grey belong to the opponent (red in the game), and light grey planets belong to no player. The triangles are fleets, and the numbers (in planets and triangles) represent the
starships.}
\end{figure}

Moreover, the bot's design faces two major problems: the first one \cite{doc1}is that the bot can't store any information about its previous turns like actions it did, actions of its opponent or even the map's state. Since in each turn, the bot meets with an unknown map as it just begins the game for the first time. The second one\cite{doc3} is that the time requires to move(make an action) is just one second. So these difficulties make the bot's design like a great challenge. In this kind of game, everything has a sum of properties\cite{doc1}. Such as, planets have the x and y coordination for their locations in the map, ownersID, number of starship and growth rate. To conquest other planets, the player needs to send fleets for this aim.Each fleet has a playerID parameter, number of starships, source planetID, destination planetID, turn's number need to reach the target. In each simulated turn\cite{doc1}, the player has the ability to send fleets in a battle with other planet's starships with the source planetID and target planetID, while, the player has the ability\cite{doc1} to make just one action per turn. After each move (action) the planets belong to the players\cite{doc5} increase their ship's number according to their growth rate. To make fleets previously sent reach enemies planets its take time of many turns according to the distance between the source planet and the target planet, moreover, if the source and target planet owned by the same player then it considered like a reinforcment\cite{doc1,doc5} by adding the ship's number on the fleet to the number hosted on the target planet. when the fleets reach the target its will make battles with local target ships, otherwise, if the target is a neutral planet, the player must to sends at least one additional ship to own the planet. While, if the target is owned by the enemy the two players will fight until one with the highest starship number owns the planet. When the player sent fleets to reach some goals\cite{doc5}, he can't change their directions. In addition, the player can send more fleet in the next turns even that the first ones do not yet arrive at their destinations. In the end of the match\cite{doc5}, the player with the highest number of starships wins. If a player loses all their starships then the game will end also faster. whilst, the players have the same starship's number at the end of the game there is a draw\cite{doc5}. 
\section{immune system overview}

@@

\begin{figure}
\begin{tabular}{c}
\includegraphics[scale = 0.8]{clonaS}
\end{tabular}
\caption{Clonal selection mechanism}
\end{figure}

@@

\subsection{Artificial Immune System}
Inspiring from the biological immune system an algorithm has been developed called Artificial Immune System (AIS)\cite{doc6}. The search technic is similar to the natural immune system by the implication between the fitness function and the affinity maturation in the natural system.
\subsubsection{Initialisation}
A random population N is generated in the search space, as a process that used in the other heuristic algorithms. This population considered like antibodies.
\subsubsection{Clonal proliferation}
In this step, the antibodies will clone (proliferate) according to their fitness(affinity).
\subsubsection{Maturation}
The maturation technic is similar to the mutation one with a mutation probability P. this mutation is applied to equation (1) : 
\begin{equation}
x_{id} = x_{id} + k(x_{d_{max}} - x_{d_{min}}) . N(0,1)
\end{equation}
where $x_{id}$ represent the dimension d of the antibody i, $x_{max}$ and $x_{min}$ represent the min and the max bounds of the variable i, N(0,1) is the standard distribution and k is the scale factor.
\subsubsection{Evaluation}
In the evaluation step, the fitness function of every antibody is calculated by computing the affinity values.
\subsubsection{Ageing operator}
This factor is used to eliminate the individuals lost more. Indeed, the Ageing operator leads to upgrading the initial population.
\subsubsection{Selection process}
This section will be applied to select N individual to the next generation. 
%\subsection{AIS pseudocode}
%\begin{enumerate}
%\item initialize N individual with random values between 0 and 1.
%\item For iteration = 1 : maxIteration,
%\begin{itemize}
%\item Compute the affinities.
%\item Clone the antibodies.
%\item Mutate the antibodies cloned in the previous step.
%\item Compute the affinities for the new antibodies mutated.
%\item Applied the selection process to select the next generation
%\end{itemize} 
%End For \\
%Display the optimal solutions. \\
%End
%\end{enumerate}
\begin{figure}
\begin{tikzpicture}[scale = 0.8]
\draw [thick] (4.5,20) circle [radius=0.5];
\node at (4.5,20) {Start};
\draw [->] [thick](4.5,19.5) -- (4.5,19);
\draw (2,19) --(8,19);
\draw (1,18.5) --(7,18.5);
\draw (2,19) --(1,18.5);
\draw (8,19) --(7,18.5);
\node at (4.5,18.7) {AIS parameters};
\draw [->] [thick](4.5,18.5) -- (4.5,18);
\draw (1,18) --(8.5,18);
\draw (1,17.5) --(8.5,17.5);
\draw (1,18) --(1,17.5);
\draw (8.5,18) --(8.5,17.5);
\node at (4.5,17.7) {Random antibodies initialisation};
\draw [->] [thick](4.5,17.5) -- (4.5,17);
\draw (1,17) --(8.5,17);
\draw (1,16.5) --(8.5,16.5);
\draw (1,17) --(1,16.5);
\draw (8.5,17) --(8.5,16.5);
\node at (4.5,16.7) {Initial antibodies evaluation};
\draw [->] [thick](4.5,16.5) -- (4.5,16);
\draw (1,16) --(8.5,16);
\draw (1,15.5) --(8.5,15.5);
\draw (1,15.5) --(1,16);
\draw (8.5,15.5) --(8.5,16);
\node at (4.5,15.7) {Clonal proliferation};
\draw [->][thick] (4.5,15.5) -- (4.5,15);
\draw (1,15) --(8.5,15);
\draw (1,14.5) --(8.5,14.5);
\draw (1,14.5) --(1,15);
\draw (8.5,14.5) --(8.5,15);
\node at (4.5,14.7) {Maturation};
\draw [->][thick] (4.5,14.5) -- (4.5,14);
\draw (1,14) --(8.5,14);
\draw (1,13.5) --(8.5,13.5);
\draw (1,13.5) --(1,14);
\draw (8.5,13.5) --(8.5,14);
\node at (4.5,13.7) {Mutated antibodies evaluation};
\draw [->][thick] (4.5,13.5) -- (4.5,13);
\draw (1,13) --(8.5,13);
\draw (1,12.5) --(8.5,12.5);
\draw (1,12.5) --(1,13);
\draw (8.5,12.5) --(8.5,13);
\node at (4.5,12.7) {best individuals selection};
\draw [->][thick] (4.5,12.5) -- (4.5,12);
\draw (4.5,12) --(2.5,11.5);
\draw (2.5,11.5) --(4.5,11);
\draw (4.5,11) --(6.5,11.5);
\draw (6.5,11.5) --(4.5,12);
\node at (4.5,11.5) {Stopping criterion};
\draw (2.5,11.5) --(0.7,11.5);
\draw (0.7,11.5) --(0.7,17.3);
\node at (4.1,10.7) {Yes};
\node at (2.2,11.8) {No};
\draw [->][thick] (0.7,17.3) -- (4.5,17.3);
\draw [->][thick] (4.5,11) -- (4.5,10.5);
\draw (1.5,10.5) --(7.5,10.5);
\draw (1.5,9.8) --(7.5,9.8);
\draw (1.5,10.5) --(1.5,9.8);
\draw (7.5,10.5) --(7.5,9.8);
\node at (4.5,10.1) {Output optimal solution};
\draw [->][thick](4.5,9.8) -- (4.5,9.3);
\draw [thick](4.5,8.8) circle [radius=0.5];
\node at (4.5,8.8) {End};
\end{tikzpicture}
\caption{AIS diagram}
\end{figure}

\section{AisBot: the Canquer Bot}
In the previous sections, we explained that there are two primary constraints in the development of the bot's behaviours. The main constraint is the limited time available for the bot to move (1 second). The second fundamental constraint that is no information could be stored from the previous turns. Based on these two major restrictions, the design performance and the implementation possibilities are limited. However, some researchers have been carried out on the memory solutions based on metaheuristic algorithms to make the bot store some information from its previous actions to determine the next move, but most of them are limited by the time factor; the performance of an EA is limited by time, is almost impossible to run an EA in each step of time (1 second). For the bot's behaviour evaluation it is no possible to improve an action without any feedback from one turn to the next. \\
The purpose of this investigation is to obtain data which will help to address those research restrictions, while these data were collected using a set of rules in order to optimize the bot's behaviour. \\
Anyway, in this case of study, we have to perform a single action mode: send starships from a planet to another; to make fleets move in the map, the bot should distinguish between self-planets and the enemy's planets. Based on this simple action, one of the greatest challenges is to determine which planet that will generate the fleets, how many starships will include on it and what is the planet will be targeted. In the next, we will describe our bot's behaviour, following the definition of the parameters used in the optimization. Finally, we will explain the technics governing the bot.

\subsection{AisBot}

\includepdf[scale=0.7,pages=1]{botDiagram}

As we mentioned previously, the purpose of this study is to try to optimize the behaviour of a bot during the planet war RTS game. In order to improve our experimentation, we use the AisBot as a conquer bot in this game, and it works as follows: first of all, when a turn is started, the bot tries to determine the base planet based on a score function and the rest of planets are used as colonies.Secondly, the bot decides which planet to attack for the next turn or if it owns additional planet the action will be considered as a reinforcement, in order to reach the target planet, it can take some number of turns. If the bot trying to attack a target is owned by a neutral, the action will be considered as an expansion; however, if it's owned by the enemy, the action will be considered as a conquest. Once the base planet is reinforced by starships coming from colonies, the action will be considered as a Tith. In addition, when colonies that are closed to the target planet than the base is allowed to attack the target by sending fleets, instead of reinforcing the base and this one sends those fleets to the target planet, but move directly to the target. Besides, when a planet was targeted by the bot, it is no possible to decide another attack against the same planet until the first one finished, that is mean, for each fleet sent to perform an attack, it knows the target planet in its data structure. \\

In order to improve the behaviour of the bot,  a set of rules is defined included some parameters classified by weights, probabilities and amounts. the parameters signification is : 
\begin{itemize}
\item \textit{$Tith_{perc}$}: starships proportions that the bot can sends.
\item \textit{$Tith_{prob}$}: Tith probability that a colony sends to the base planet.
\item \textit{$w_{NS}$}: weight of starships number hosted on the planet.
\item \textit{$w_{DIS}$}: weight of distance between the base and the target planet.
\item \textit{$w_{GR}$}: weight of growth rate according to the target planet.
\item \textit{$Pool_{perc}$}: percentage of extra starships can send from the base to the target planet.
\item \textit{$Support_{perc}$}: Percentage of extra starships from the colony to the target.
\item \textit{$Support_{prob}$}: Probability of sending extra starships from the colony to the target.
\end{itemize}
Furthermore, each parameter takes some values during the optimization process depends on it meaning in the game, our conquer bot will be based on these values to make decisions during the game. To determine the target planet the bot will use a score function define as follow:

\begin{equation}
Score(p) = \frac{p.NumStarships.w_{NS-DIS}.Dist(base,p)}{1+p.GrowthRate.w_{GR}}
\end{equation}

Where the $w_{NS-dis}$ and the $w_{GR}$ are weights related successively to starships number, the growth rate for the planet and the distance to reach the target. As we mentioned above the $base$ is the planet which has the highest number of starships and $p$ refer to planet want to evaluate. \\

When the Tith and the attack process are performed by the colonies, the base planet also sends starships to attack the target. The number of starships sends to attack is estimated according to the attack mode, if the bot attack mode is expansion where the target does not generate starships during the game that implies the bot will integrate a very specific starships number to be able to defeat the planet target, in the other hand, if the bot attack mode is a conquest, the engine will estimate the number of troops needs to beat the enemy.

\subsection{RandomBot}
The development kit of google for the planet war game include an example of a bot called RandomBot, the behaviour of this bot is very simple and it works independently of any situation (map). based on it basic behaviour, the bot tries to send fleets randomly and try to perform random attacks without any estimation.If we compare the AisBot and the RandomBot behaviours, we will clearly find that the AisBot behaviour is more complex than the one on RandomBot, and it be able to defeat it in all situation and maps; however, it needs more turns to beat it; for this purpose, the greatest challenge is to make the AisBot's behaviour quite fast by determining the values of parameters shown in the previous section systematically.

\section{AisBot: an AIS optimization}
The aim of this optimization is to make the bot behave faster and be able to win in less number of turns, in order to do that, an artificial immune system (AIS) algorithm used on the set of rules included the parameters that will determine the behaviour of the bot; when the parameters are improved, they are fixed and will be uploaded by the bot in order to play a real scenario. \\
Therefore, the purpose is to determine the parameters values in order to evaluate the bot's behaviour.The AIS proposed in this study use a floating array to represent all parameters defined previously, while, the clonal proliferation process works on a totally new array with a specific proliferation factor for each parameter according to its fitness. The maturation mechanism is applied to the cloned antibodies by mutating the parameters values using the equation (1) with a probability amount to minimize the bad antibodies. \\

The selection process based on an evaluation technic by implementing tournaments where each cloned individual used to compete with the aim of being selected for the next generation from the best results were chosen. The evaluation of an individual is staged by including their parameters for the AisBot behaviour and placing the bot on a real planet war game against the RandomBot on five maps. \\

The aim of this optimization is to minimize the number of turns needs to win, the best bot is the one that plays fewer turns until win; this kind of ranking bots strongly shown a constraint problem is that each individual was able to win every single game.

\section{Exprementation and results}
With the aim of testing the CLONALG algorithm, the bot placed under several situations and play several games against the RandomBot. The algorithm parameters can be found on the Table 1:
\begin{table}[h!]
\centering
\begin{tabular}{ |c|c| }
\hline
 Number of antibodies & 20 \\ 
 Number of generations & 15 \\  
 maximun antbodies Cloned & 72 \\ 
 \hline   
\end{tabular}
\caption{Parameters used in the CLONALG algorithm}
\label{TABLE 1}
\end{table}

To make a bot under a real game scenario with optimized parameters will take hours, since, to evaluate each individual it took more seconds. The figure (4) showed the evaluation of the number of turns plays by the bot until win, and it appears that the number of turns needs to win in five maps decrease when the evaluation progress.Furthermore, in figure (5) two, the parameters evaluation is shown during the optimization process in amoung fifteen generations. \\

\begin{figure}
\begin{center}
\begin{tikzpicture}
\begin{axis}[
    title={Turns number evaluation},
    xlabel={Generation},
    ylabel={Turns},
    xmin=0, xmax=16,
    ymin=0, ymax=800,
    xtick={0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15},
    ytick={150,300,450,600,750},
    legend pos=north west,
    ymajorgrids=true,
    grid style=dashed,
]

\addplot[
    color=blue,
    mark=square,
    ]
    coordinates {
    (1,598)(2,597)(3,557)(4,624)(5,581)(6,528)(7,585)(8,580)(9,650)(10,538)(11,588)(12,605)(13,569)(14,562)(15,552)
    };
    \legend{turns by generation}

\end{axis}
\end{tikzpicture}
\end{center}
\caption{the evaluation of the number of turns plays by the bot until win in 5 maps, and it appears that the number of turns needs to win in five maps decrease when the evaluation progress}
\end{figure}

\begin{figure}
\begin{center}
\begin{tikzpicture}[scale = 0.8]
\begin{axis}[
    title={Turns number evaluation},
    xlabel={Generation},
    ylabel={Turns},
    xmin=0, xmax=16,
    ymin=0, ymax=1,
    xtick={0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15},
    ytick={0.15,0.3,0.45,0.6,0.75,0.9},
    legend pos=outer north east,
    ymajorgrids=true,
    grid style=dashed,
]

\addplot[
    color=blue,
    ]
    coordinates{(1,0.651)(2,0.369)(3,0.713)(4,0.427)(5,0.721)(6,0.614)(7,0.34)(8,0.395)(9,0.82)(10,0.216)(11,0.577)(12,0.234)(13,0.7)(14,0.175)(15,0.845)};

    \addplot[
    color=red,
    ]
    coordinates{(1,0.651)(2,0.344)(3,0.616)(4,0.79)(5,0.33)(6,0.508)(7,0.649)(8,0.097)(9,0.419)(10,0.85)(11,0.151)(12,0.635)(13,0.646)(14,0.601)(15,0.057)};

    \addplot[
    color=green,
    ]
    coordinates{(1,0.665)(2,0.515)(3,0.483)(4,0.13)(5,0.528)(6,0.771)(7,0.755)(8,0.553)(9,0.672)(10,0.978)(11,0.161)(12,0.602)(13,0.186)(14,0.997)(15,0.447)};

    \addplot[
    color=purple,
    ]
    coordinates{(1,0.122)(2,0.949)(3,0.603)(4,0.481)(5,0.619)(6,0.817)(7,0.871)(8,0.31)(9,0.552)(10,0.837)(11,0.703)(12,0.41)(13,0.102)(14,0.02)(15,0.323)};

    \addplot[
    color=gray,
    ]
    coordinates{(1,0.785)(2,0.425)(3,0.318)(4,0.714)(5,0.975)(6,0.746)(7,0.245)(8,0.439)(9,0.426)(10,0.449)(11,0.912)(12,0.301)(13,0.703)(14,0.138)(15,0.124)};

    \addplot[
    color=black,
    ]
    coordinates{(1,0.113)(2,0.029)(3,0.654)(4,0.132)(5,0.144)(6,0.364)(7,0.226)(8,0.379)(9,0.3)(10,0.393)(11,0.336)(12,0.149)(13,0.642)(14,0.054)(15,0.814)};

    \addplot[
    color=orange,
    ]
    coordinates{(1,0.64)(2,0.259)(3,0.674)(4,0.127)(5,0.875)(6,0.258)(7,0.067)(8,0.589)(9,0.907)(10,0.166)(11,0.308)(12,0.789)(13,0.587)(14,0.272)(15,0.636)};

    \addplot[
    color=brown,
    ]
    coordinates{(1,0.366)(2,0.685)(3,0.046)(4,0.602)(5,0.674)(6,0.212)(7,0.176)(8,0.949)(9,0.86)(10,0.807)(11,0.645)(12,0.361)(13,0.096)(14,0.712)(15,0.32)};

    \legend{$Tith_{perc}$,$Tith_{prob}$,$W_{NS}$,
    $W_{GR}$,$W_{DIS}$,$Pool_{perc}$,$Support_{perc}$,$Support_{prob}$}

\end{axis}
\end{tikzpicture}
\end{center}
\caption{the evaluation of the Parameters during the optimization process}
\end{figure}
